---
title: "Linear Regression exercise"
output: html_notebook
---

# Exercise 1

Consider the titanic dataset. Fit a linear regressor to predict the values of 
Fare from the values of Survived,Pclass, Sex and Age

```{r}
library(titanic)
(reg <- lm(Fare ~ Survived+Pclass+Sex+Age, titanic_train))
summary(reg)
library(ggResidpanel)
ggResidpanel::resid_panel(reg, plots = c('resid'))

(reg <- lm(Fare ~ Pclass + Sex + Age, titanic_train))
summary(reg)
ggResidpanel::resid_panel(reg, plots=c('resid'))
```

# Exercise 2
Repeat the previous exercise using backward elimination. Is the final set of variables different from the one found in the previous exercise.
```{r}
(reg <- lm(
  Fare ~ PassengerId+Survived+Pclass+Sex+Age+SibSp+Parch+Ticket+Cabin+Embarked, 
  titanic_train
  ))
summary(reg)
```
The variable Ticket has the higher p value 0.99, lets remove it and fit the 
model again:
```{r}
(reg <- lm(
  Fare ~ PassengerId+Survived+Pclass+Sex+Age+SibSp+Parch+Cabin+Embarked, 
  titanic_train
  ))
summary(reg)

```
```{r}
(reg <- lm(
  Fare ~ PassengerId+Survived+Pclass+Sex+Age+SibSp+Parch+Embarked, 
  titanic_train
  ))
summary(reg)
```
```{r}
(reg <- lm(
  Fare ~ Survived+Pclass+Sex+Age+SibSp+Parch+Embarked, 
  titanic_train
  ))
summary(reg)
```
```{r}
(reg <- lm(
  Fare ~ Survived+Pclass+Sex+Age+SibSp+Parch, 
  titanic_train
  ))
summary(reg)
```
```{r}
(reg <- lm(Fare ~ Pclass+Sex+Age+SibSp+Parch, titanic_train))
summary(reg)
```
All variables are now statistically relevant. The backward elimination process 
is finished. We can now conclude showing the residual plot:
```{r}
resid_panel(reg, plot='resid')
```
The residual are overall random (even if not perfectly so). The result is 
acceptable.

# Exercise 3
Consider the titanic dataset. Fit a linear regressor to predict the values of 
Age from the values of Survived, Pclass, Sex and Fare.
```{r}
(reg <- lm(Age ~ Survived+Pclass+Sex+Fare, titanic_train))
summary(reg)
```
Sex is a irrelevant variable so lets remove it:
```{r}
(reg <- lm(Age ~ Survived+Pclass+Fare, titanic_train))
summary(reg)
```

# Exercise 4
Repeat the previous exercise using backward elimination. Is the final set of 
variables different from the one found in the previous exercise
one found in the previous exercise.
```{r}
(reg <- lm(
  Age ~ PassengerId+Survived+Pclass+Sex+Fare+SibSp+Parch+Ticket+Cabin+Embarked, 
  titanic_train
  ))
summary(reg)
```
```{r}
(reg <- lm(
  Age ~ PassengerId+Survived+Pclass+Sex+Fare+SibSp+Parch+Cabin+Embarked, 
  titanic_train
  ))
summary(reg)
```
```{r}
(reg <- lm(
  Age ~ PassengerId+Survived+Pclass+Sex+Fare+SibSp+Parch+Embarked, 
  titanic_train
  ))
summary(reg)
```
```{r}
(reg <- lm(
  Age ~ Survived+Pclass+Sex+Fare+SibSp+Parch+Embarked, 
  titanic_train
  ))
summary(reg)
```
```{r}
(reg <- lm(
  Age ~ Survived+Pclass+Fare+SibSp+Parch+Embarked, 
  titanic_train
  ))
summary(reg)
```
```{r}
(reg <- lm(
  Age ~ Survived+Pclass+Fare+SibSp+Parch, 
  titanic_train
  ))
summary(reg)
```
```{r}
(reg <- lm(
  Age ~ Survived+Pclass+Fare+SibSp, 
  titanic_train
  ))
summary(reg)
```

# Exercise 5
Consider the Boston dataset. Fit a linear regressor to predict the values of 
crim from the values of the other variables.
```{r}
library(MASS)
str(Boston)
Boston$chas<-factor(Boston$chas)
levels(Boston$chas)
Boston$rad<-factor(Boston$rad)
levels(Boston$rad)
(reg <- lm(
  crim ~ zn+indus+chas+nox+rm+age+dis+rad+tax+ptratio+black+lstat+medv, 
  Boston
  ))
summary(reg)
```
remove irelevent value starting from the most p value:
```{r}
(reg <- lm(
  crim ~ zn+indus+chas+nox+rm+dis+rad+tax+ptratio+black+lstat+medv, 
  Boston
  ))
summary(reg)
```
```{r}
(reg <- lm(
  crim ~ zn+indus+chas+nox+rm+dis+tax+ptratio+black+lstat+medv, 
  Boston
  ))
summary(reg)
```
```{r}
(reg <- lm(
  crim ~ zn+indus+chas+nox+rm+dis+tax+black+lstat+medv, 
  Boston
  ))
summary(reg)
```
```{r}
(reg <- lm(
  crim ~ zn+indus+nox+rm+dis+tax+black+lstat+medv, 
  Boston
  ))
summary(reg)
```
```{r}
(reg <- lm(
  crim ~ zn+indus+rm+dis+tax+black+lstat+medv, 
  Boston
  ))
summary(reg)
```
```{r}
(reg <- lm(
  crim ~ zn+indus+dis+tax+black+lstat+medv, 
  Boston
  ))
summary(reg)
```


