---
title: "Exam example2"
author: "Anahita Esfandiaryfard"
output: 
  pdf_document: default
  html_notebook: default
---
# Question1
```{r}
str(infert)
```
The dataframe contains 248 data and 8 variables.We can check if there are any 
na value as follows,
```{r}
any(is.na(infert))
```
The dataframe does not contain any na values.

# Question2
```{r}
aggregate(infert['age'], list(education=infert$education), mean)
```
the group containing the older subject is 0-5yrs.

# Question 3
```{r}
library(ggplot2)
ggplot(infert, aes(x=education, fill=education))+geom_bar(aes(y=..count../sum(..count..)))+ ylab("frequency")
```
according to bar plot class 6-11 yrs has more subject.

# Question 4
```{r}
library(tidyr)
infert.long <- gather(infert, key='Variable', value='Value',
    age, parity, induced, case, spontaneous, stratum, pooled.stratum
)

ggplot(infert.long, aes(x=Variable, y=Value, fill=Variable)) +
  geom_boxplot()
```
Since the variables vart different range it is better to split the boxplot into two parts:
```{r}
ggplot(subset(infert.long, 
              Variable %in% c("case", "induced", 'parity', 'spontaneous')), 
       aes(x=Variable, y=Value, fill=Variable)) +
  geom_boxplot()
```
```{r}
ggplot(subset(infert.long, 
              Variable %in% c("age", "pooled.stratum", 'stratum')), 
       aes(x=Variable, y=Value, fill=Variable)) +
  geom_boxplot()
```
The distributions of `age` and `stratum` are overall symetric. Indeed, the box and the whiskers are symmetric with respect to the median value. `case`, `induced` and `spontaneous` are not symmetrical. `pooled.stratum` is not perfectly symmetric but still not completly asymmetric. `parity` is not symmetric because the bottom whisker does not extend below the box.

None of the variables has outliers.

# Question 5
The following code compute the correlation matrix.removing the first columns 
which are factors:
```{r}
(c <- cor(infert[-c(1)]))
```
To easily check what is the strongest relationship, I will use corrplot:
```{r}
library(corrplot)
corrplot.mixed(c)
```
 * `stratum` - `pooled.stratum`: this is a strong correlation, with a correlation coefficient of $0.75$;
 * `parity` - `induced`: this is a moderate correlation, with a correlation coefficient of $0.45$;
 * `case` - `spontaneous`: this is a moderate correlation, with a correlation coefficient of $0.36$;
 * `parity` - `spontaneous`: this is a moderate correlation, with a correlation coefficient of $0.31$;
 
The other positive correlations are weak (below $0.3$).

The strongest negative correlation is:

 * `stratum` - `parity`: this is a moderate negative correlation, with a correlation coefficient of $-0.31$;

The other negative correlations are weak (absolute value below $0.3$).

# Question 6
```{r}
cor.test(infert$induced, infert$parity)
```
The p-value is below the significant level so the alternative hypothesis will be 
rejected.The correlation is significantly significant.

# Question 7
Let us compute the table of proportion for case:
```{r}
counts <- table(infert$case)
prop.table(counts)
```
The proportion of observations for which `case=0` is $0.67$. We can run a statistical test to check if this estimated proportion is significantly different than $0.5$.

```{r}
prop.test(counts, p=0.5)
```

The p-value is below the significance threshold, so we accept the alternative hypothesis that the observations are not evenly distributed with respect to case.

# Question 8
```{r}
(reg <- lm(parity ~ induced, infert))
```
If we observe a value of `induced` increased by $1$ unit, we would expect to observe an increment of `parity` by $0.756$ units.

# Question 9 
```{r}
ggplot(infert, aes(x=induced, y=parity))+ geom_point()+geom_smooth(method = lm)
```
 
 # Question 10
```{r}
summary(reg)
```
We will also display the residual plot to check if the regressor is a good fit:

```{r}
library(ggResidpanel)
resid_panel(reg, plots='resid')
```
From the residual plot, it is clear that the fit is not good. Indeed, the residuals do follow a pattern (they are not random) and they are not small. This is also confirmed by the $R^2$ which is below $0.2$.

Even if the regressor is not a good fit, it is statistically significant. This can be assessed by observing that the p-value of the F-test is below the significance threshold of $0.05$. Also, all the paramter estimates are statistically significant (p-values below $0.05$).
