---
title: "Exercise 06"
description: 
  "Create an R Notebook which explains how to compute the volume of a        pyramid (you can use the web to get help!). Use headers to define         sections and subsections and R cells to input code and show the results    of the computations. Try to break the computations into different parts    (avoid a single long R cell) to guide the reader. This is how you will    learn to present R data analyses."
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

# Introduction
A pyramid is a solid and its volume represents the amount of space it occupies. In general, its base can be any polygon, but we will see only the case of a square pyramid, i.e., a pyramid with a square base. The general formula for computing the volume of a Pyramid is as follows:

$$ V = \frac{1}{3} Bh $$

where $B$ is the area of the base and h is the height of the pyramid.

## Example
Find the volume of a regular square pyramid with base sides $10cm$ and height $18cm$.

Let's first compute $B$:

$$ B = 10 cm \times 10 cm = 100 cm^2 $$

Let's now apply the formula to compute the volume:


$$ V = \frac{1}{3} B h = \frac{1} {3} 100 cm^2 \times 18 cm $$

### R code
Let's see how to do it in R code. We first assign values to the *s* and *h* variables:

```{r}
s <- 10
h <- 18
```

We now compute the area of the base:

```{r}
B <- s * s
```

Finally, we compute the volume using the formula discussed above:

```{r}
(V <- (1/3) * B * h)
```

